A Gentle Introduction into Structural Causal Models

### 2021-06-02 draft.Rmd
draft

**Established Conditions:**

*Definition:***Independence**

@@

>>>>

Definition:Independence

*The causal generative process of a system’s variables is composed of autonomous modules that do not inform or influence each other.*
*In the probabilistic case, this means that the conditional distribution of each variable given its causes (i.e., its mechanism) does not inform or influence the other conditional distributions*,
*In case we have only two variables, this reduces to an independence between the cause distribution and the mechanism producing the effect distribution* [@peters_elements_2017].

@@

**Established Conditions for counterfactuals:**
